Graphical tests for coverage [@sailynoja2021graphical]

### 2021-12-01 docs/30-11-21_coverage/coverage.Rmd
This is wrong way around as pointed out during presentation

| Analyst   | $n$ | Inside the CrI | Empirical coverage | Diagnosis |
| --------- | --- | -------------- | ------------------ | --------- |
| Hai Kon   | 28  | 27             | 96%                | Overconfident |
| Relan     | 28  | 21             | 75%                | Underconfident |

>>>>

| Analyst   | $n$ | Inside the CrI | Empirical coverage | Diagnosis |
| --------- | --- | -------------- | ------------------ | --------- |
| Hai Kon   | 28  | 27             | 96%                | Underconfident |
| Relan     | 28  | 21             | 75%                | Overconfident |
